|

### 2020-04-21 analysis/paper/manuscript.Rmd
Tweaks too the MS for CJFAS "First Look" steps

@@

```{r map, echo = FALSE, fig.cap = 'A screen shot of cod tag mapping tool using shinydashboard and leaflet. The markercluster function dynamically splits or pools tagging locations (red, orange, green or yellow points) depending on zoom level, the recovery positions (blue) are much fewer, and are left to be plotted individually at all scales. Options to include pop up labels are included, so specific information on each point can be retrieved with a mouse click (in this case: tag number, fish length, date released, and date recovered), which is particularly useful when error checking.'}
knitr::include_graphics("figures/tagging_dashboard_map_tab.png")
```

```{r summary, echo = FALSE, fig.cap = 'Basic summaries of the recovery data from the tags selected within the shiny dashboard cod tag mapping tool. In this case, histograms and summary statistics of the recovery positions are returned, along with a simple map of kernels showing the spatial distribution of the selected tag recoveries.'}
knitr::include_graphics("figures/tagging_dashboard_summary_tab.png")
```

>>>>

  **Keywords**: dashboard, data exploration, integrated analysis, model validation, open stock assessment

@@

```{r map, echo = FALSE, fig.cap = "A screen shot of cod tag mapping tool. The markercluster function dynamically splits or pools tagging locations (red, orange, green or yellow points) depending on zoom level, the recovery positions (blue) are much fewer, and are left to be plotted individually at all scales. Options to include pop up labels are included, so specific information on each point can be retrieved with a mouse click (in this case: tag number, fish length, date released, and date recovered), which is particularly useful when error checking. Base map created with leaflet [@cheng2018] using ESRI's Ocean BaseMap (Sources: Esri, GEBCO, NOAA, National Geographic, DeLorme, HERE, Geonames.org, and other contributors)."}
knitr::include_graphics("figures/tagging_dashboard_map_tab.png")
```

```{r summary, echo = FALSE, fig.cap = 'Basic summaries of the recovery data from the tags selected within the cod tag mapping tool. In this case, histograms and summary statistics of the recovery positions are returned, along with a simple map of kernels showing the spatial distribution of the selected tag recoveries. Base map created in R with package maps [@becker2018a] and mapdata [@becker2018b].'}
knitr::include_graphics("figures/tagging_dashboard_summary_tab.png")
```
